Alleviating the Topology Mismatch Problem in Distributed Overlay Networks

### 2014-01-28 conclusion.tex
2013.01.23 (Alex) Introduction, background and conclusion sections reworked.

Research and development for computer systems
built using the \p\ paradigm have flourished  in the last decade.
By and large, such systems exploit the loose-coupling and self-organization 
of participating nodes to shape substrates upon which diverse applications 
can run; the latter offer services including but not limited to 
distributed naming, 
Internet telephony and video conferencing, 
storage and indexing, 
content and file sharing, 
web crawling and caching, 
event notification and subscribe/publish.
These services are provided atop the 
best-effort infrastructure of today's Internet 
and they have to effectively deal with an array of key issues
emanating from the fact that \p\ nodes 
operate at the edge of the Internet; such critical issues include
node availability, robustness, scalability, load-sharing,
quality-of-service and user anonymity.
The majority of such issues emerges as 
application-level \p--networks are formed without paying 
adequate attention to the design of the physical network beneath.
The latter constitutes what is known as the
topology mismatch problem between the \p-overlays and the physical networks.
In addition, the development of \p--systems and applications
typically involved juggling a set of tradeoffs (e.g.,
choosing higher accuracy at the cost of increased system overhead.)

% Computer systems design is typically about juggling a set of tradeoffs (e.g.,
% choosing higher accuracy at the cost of increased system overhead.)  
In surveying more than
a decade's worth of research efforts aimed at solving the topology mismatch
problem in both unstructured and structured \p\ networks, we find this
tussle-of-tradeoffs property to hold.  
With regards to the three criteria we used --efficiency,
overhead, and scalability-- we find that none of the proposed solutions 
is superior to the others on all three fronts.  This is not surprising.
Nonetheless, by
1)~presenting an analysis of each of the solutions, 
including what distinguishes it from the
others and its advantages and disadvantages and 
2)~offering a pictorial
comparison of how each solution fares compared with the others with regards
to efficiency, overhead, and scalability, we hope to have provided \p\
researchers and developers with enough perspective so that depending 
on the needs of their particular application, they are able to select
amongst these surveyed solutions or propose a new solution of their own.

>>>>

Research and development on application systems that follow the 
\p\ architectural paradigm, have flourished over the last decade.
By and large, such systems exploit the loose-coupling and self-organization 
of participating nodes to shape substrates upon which diverse applications 
can run; the latter offer services including, but not limited to, 
distributed naming, 
Internet telephony and video conferencing, 
storage and indexing, 
content and file sharing, 
web crawling and caching, 
event notification and subscribing/publishing.
These services are provided atop the 
best-effort infrastructure of today's Internet;
services have to comply with an array of key requirements and 
offer quality attributes that include node availability, robustness,
scalability, load-sharing, quality-of-service and user anonymity. 
%%AD rephrased below as above - too long sentence it was!
% and they have to effectively deal with an array of key quality attributes that
% they may need or have to offer node availability, robustness,
% scalability, load-sharing, quality-of-service and user anonymity.
%%
The difficulty to handle such characteristics effectively, 
emanates from the fact that
peers  operate at the edge of the Internet and no 
adequate attention is paid to the structure of the physical network 
during application-level network design. 
The deviation of the logical distributed overlay formation from the 
physical network yields suboptimal use of the underlying 
infrastructure and is known as the topology mismatch
problem.
%%AD rephrased what is below as above..
% The deviation of the structure of the overlay network from the
% optimal, according to the underlying physical structure, constitutes what is
% termed topology mismatch and the problem is known as the topology mismatch
% problem.

Development of \p--systems and applications
typically involve juggling a set of tradeoffs (e.g.,
choosing higher accuracy at the cost of increased system overhead).
% Computer systems design is typically about juggling a set of tradeoffs (e.g.,
% choosing higher accuracy at the cost of increased system overhead.)  
In surveying more than
a decade's worth of research efforts aimed at solving the topology mismatch
problem in both unstructured and structured \p\ networks, we find this
tussle-of-tradeoffs property to hold.  
With regards to the three criteria we used --efficiency,
overhead, and scalability-- we find that none of the proposed solutions 
is superior to the others on all three fronts.  This is not surprising.
Nonetheless, by
\begin{inparaenum}[\itshape i\upshape)]
  \item presenting an analysis of each of the solutions,
including what distinguishes it from the
others and its pros and cons and
  \item offering a pictorial
comparison of how each solution fares in regards to others as far as
efficiency, overhead, and scalability are concerned,
\end{inparaenum}
we hope to have provided \p\
developers and researchers with enough insight and perspective;
as they face specific problems, they will be readily able to 
draw the best possible design decisions for their own application
environments.
%%AD sentence was too long - this "giant" thing to much ass-kissing... no.
% when facing a specific problem, they would 
% when they face a specific problem, th 
% so that depending
% on the particular problem in hand, they are able to make a
% correct choice amongst these surveyed here or, by firmly standing on
% the shoulders of giants, propose a new solution of their own.

### 2014-01-28 intro.tex
2013.01.23 (Alex) Introduction, background and conclusion sections reworked.

The peer-to-peer paradigm gave impetus to two ``killer'' applications:
file-sharing and Internet telephony.
The {\sl Napster} file-sharing was widely acknowledged as the 
``fastest growing Internet application ever'' in $2001$ when
$26$ million users shared $80$ million songs.
% File-sharing, originally introduced by
% {\sl Napster} (Section~\ref{section:background}), was widely
% acknowledged by $2001$ as the ``fastest growing Internet application ever" 
% with $26$ million users sharing $80$ million songs.
% % at the height of its popularity. 
Other file-sharing applications followed suit, 
including {\sl Gnutella} and {\sl Limewire} enjoying $3$ 
million concurrently-connected peers as well as 
{\sl BitTorrent} connecting over $150$ million users by the end of $2006$.
\p\ telephony saw explosive growth with the advent of {\sl Skype}.
Since its introduction in $2003$,
{\sl Skype} has become extremely popular with more than $650$ million users 
in $2011$~\cite{skypetotalusers}; on March $5$th, $2012$,  
the astonishing figure of $35$ million concurrently-online users  
was reported~\cite{skypesymusers}.
%%
In addition, a startling number of diverse and successful
applications have been built based on a \p\ architecture. Some of them include:
distributed search engines~\cite{yaci}, 
distributed data-storage systems~\cite{kbc_oceanstore_2000,bdet_fsdfs_2000,dkkms_cfs_2001,dr_pastutility_2001,abc_farsite_2002,mmfc_ivy_2002,arla,agebh_dks_2003},
Web caches, archives and publishing systems~\cite{ird_squirrel_2002,bags_youserv_2002,wrc_publius_2000,wm_tangler_2001},
messaging applications~\cite{threedegrees}, 
event-notification infrastructures~\cite{rkcd_scribe_2001,cdkr_scribe_2002,agebh_dks_2003}, 
naming services~\cite{cmm_chorddns_2002}, 
censor-resistant stores~\cite{cswh_freenet_2001} and
lately, even cloud-based platforms~\cite{mgpj_cloudsnap_2011}.

>>>>

The peer-to-peer paradigm gave impetus to two ``killer'' applications:
file-sharing and Internet telephony.
The {\sl Napster} file-sharing was widely acknowledged as the 
``fastest growing Internet application ever'' in $2001$ when
$26$ million users shared $80$ million songs.
% File-sharing, originally introduced by
% {\sl Napster} (Section~\ref{section:background}), was widely
% acknowledged by $2001$ as the ``fastest growing Internet application ever" 
% with $26$ million users sharing $80$ million songs.
% % at the height of its popularity. 
Other file-sharing applications followed suit, 
including {\sl Gnutella} and {\sl Limewire} enjoying $3$ 
million concurrently-connected peers as well as 
{\sl BitTorrent} connecting over $150$ million users by the end of $2006$.
\p\ telephony saw explosive growth with the advent of {\sl Skype}.
Since its introduction in $2003$,
{\sl Skype} has become extremely popular with more than $650$ million users 
in $2011$~\cite{skypetotalusers}; on March $5$th, $2012$,  
the astonishing figure of $35$ million concurrently-online users  
was reported~\cite{skypesymusers}.
%%
In addition, a startling number of diverse and successful
applications have been built based on a \p\ architecture. 
Some of them include:
distributed search engines~\cite{yaci}, 
distributed data-storage systems~\cite{kbc_oceanstore_2000,bdet_fsdfs_2000,dkkms_cfs_2001,dr_pastutility_2001,abc_farsite_2002,mmfc_ivy_2002,arla,agebh_dks_2003},
Web caches, archives and publishing systems~\cite{ird_squirrel_2002,bags_youserv_2002,wrc_publius_2000,wm_tangler_2001},
messaging and dissemination applications~\cite{threedegrees,icpp08-pd}, 
event-notification infrastructures~\cite{rkcd_scribe_2001,cdkr_scribe_2002,agebh_dks_2003}, 
naming services~\cite{cmm_chorddns_2002}, 
censor-resistant stores~\cite{cswh_freenet_2001} and
lately, even cloud-based platforms~\cite{mgpj_cloudsnap_2011}.

### 2014-01-28 mard-survey.tex
2013.01.23 (Alex) Introduction, background and conclusion sections reworked.

\begin{abstract}
\emph{Peer-to-peer} (\p) systems have enjoyed immense attention and have been
widely deployed on the Internet for, well, over a decade.  
They are implemented via an overlay network abstraction, on top 
of the best-effort IP infrastructure of the Internet. 
\p\ systems offer a plethora of desirable features to 
distributed applications that are built on top of them including
anonymity, high availability and robustness, 
load balancing, quality of service, scalability, to name just a few.
Unfortunately, weaknesses of early deployments of \p\ systems, prevented 
applications from leveraging these features.
One major weakness, identified early on, is the \emph{topology mismatch problem}
between the overlay network and the underlying IP topology.
This mismatch can impose an extraordinary amount of unnecessary stress on
network resources and can adversely affect the scalability and efficiency of
applications built atop.
In this paper, we survey over a decade's worth of research efforts
aimed at alleviating the topology mismatch problem, in both unstructured
and structured \p\ systems.   
We provide a fine-grained categorization of the
proposed solutions and discuss the advantages, disadvantages, and novelties
introduced by each of them.
Finally, we provide an analysis as well as pictorial comparisons 
of the reviewed approaches, since we aim to offer a comprehensive
reference for developers, system architects and researchers in the field.
% in an attempt to provide a comprehensive quick one-stop-shop
% reference for anyone interested in the topic, from researchers and students,
% to system architects and developers.

>>>>

\begin{abstract}
\emph{Peer-to-peer} (\p) systems have enjoyed immense attention and have been
widely deployed on the Internet for well over a decade.  %% no commas here
They are implemented via an overlay network abstraction, on top 
of the best-effort IP infrastructure of the Internet. 
\p\ systems offer a plethora of desirable features to 
distributed applications that are built on top of them including
anonymity, high availability and robustness, 
load balancing, quality of service, scalability, to name just a few.
Unfortunately, inherent weaknesses of \p\ systems, prevented 
applications from leveraging these features.
One major weakness, identified early on, is the \emph{topology mismatch problem}
between the overlay network and the underlying IP topology.
This mismatch can impose an extraordinary amount of unnecessary stress on
network resources and can adversely affect the scalability and efficiency of
applications built atop.
In this paper, we survey over a decade's worth of research efforts
aimed at alleviating the topology mismatch problem, in both unstructured
and structured \p\ systems.   
We provide a fine-grained categorization of the
suggested solutions and discuss the novelty as well as 
the  advantages and disadvantages of each such proposal.
Finally, we provide an analysis as well as pictorial comparisons 
of the reviewed approaches, since we aim to offer a comprehensive
reference for developers, system architects and researchers in the field.
